---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
remotes::install_github("heike/classdata")
install.packages("ggplot2")
library(ggplot2)
data()


library(classdata)
head(ames, 50)
str(ames)
```
Q1:

Parcel ID 
chr
character with ID.

Address
chr
property address in Ames, IA.

Style
Factor
factor variable detailing the type of housing.

Occupancy
Factor
factor variable of type of housing.

Sale Date
Date
date of sale.

Sale Price
num
sales price (in US dollar).
```{include=FALSE}
max(ames$"Sale Price",na.rm=TRUE)
min(ames$"Sale Price",na.rm=TRUE)
```
range: 0 to 20500000

Multi Sale
chr
logical value: was this sale part of a package?

YearBuilt
num
integer value: year in which the house was built.
```{include=FALSE}
max(ames$"YearBuilt",na.rm=TRUE)
min(ames$"YearBuilt",na.rm=TRUE)
```
range: 0 to 2022

Acres
num
acres of the lot.
```{include=FALSE}
max(ames$Acres,na.rm=TRUE)
min(ames$Acres,na.rm=TRUE)
```
range: 0 to 12.012

TotalLivingArea (sf)
num
total living area in square feet.
```{include=FALSE}
max(ames$"TotalLivingArea (sf)",na.rm=TRUE)
min(ames$"TotalLivingArea (sf)",na.rm=TRUE)
```
range: 0 to 6007

Bedrooms
num
number of bedrooms.
```{include=FALSE}
max(ames$Bedrooms,na.rm=TRUE)
min(ames$Bedrooms,na.rm=TRUE)
```
range: 0 to 10

FinishedBsmtArea (sf)
num
total area of the finished basement in square feet.
```{include=FALSE}
max(ames$"FinishedBsmtArea (sf)",na.rm=TRUE)
min(ames$"FinishedBsmtArea (sf)",na.rm=TRUE)
```
range: 10 to 6496

LotArea(sf)
num
total lot area in square feet.
```{include=FALSE}
max(ames$"LotArea(sf)",na.rm=TRUE)
min(ames$"LotArea(sf)",na.rm=TRUE)
```
range: 0 to 523228

AC
chr
logical value: does the property have an AC?

FirePlace
chr
logical value: does the property have an fireplace?

Neighborhood
Factor
factor variable - levels indicate neighborhood area in Ames.

## 2. is there a variable of special interest or focus?

The variable of special interest in this dataset is *Total Living Area*, which reflects the total square footage of livable space in a home. This variable is important because it plays a major role in home-buying decisions and has a large impact on the Sale Price of a property


3:
```{r}
ggplot(ames, aes(x=`Sale Price`)) + geom_histogram(binwidth = 500) + ggtitle("binwidth - 500")

max(ames$`Sale Price`, na.rm=TRUE)

```
The range of the variable Sale Price is 0-20,500,000. The highest value is a very far outlier, which most Sale Price values lying between 100,000 and 500,000. Additionally, there were quite a few listed as 0.

## 4:
### Brianna
The variable I have chosen is "Year Built" and plotted it against "Sale Price" in a scatter plot. The range of this variable is from 0-2022. As the year built increases, the Sale Price generally also increases, creating a positive correlation. The oddities of far outliers listed in #3 were also noted here, with the houses having a sale price of 0 also having a 0 for Year Built. I removed these and created a second plot demonstrating this.
```{r}

ggplot(ames, aes(x=YearBuilt, y=`Sale Price`, na.rm = TRUE)) + geom_point(aes(color=factor(YearBuilt)))



ggplot(ames[which(ames$`Sale Price` < 2000) & ames$`Sale Price` > 0,], aes(x=YearBuilt, y=`Sale Price`, na.rm = TRUE)) + geom_point(aes(color=factor(YearBuilt)))
```
